Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-15 doc/ms.tex
update text about dessart PDD models and add Dessart figure to manuscript

When comparing observations of SN\,2011fe to their DD models, \citet{2014MNRAS.441..532D} find that the models are universally too faint and red at early times, $\sim$24--48\,hr after explosion.  Instead, \citet{2014MNRAS.441..532D} find that PDD models provide a better match to observations. Briefly, the diffuse material surrounding the WD heats the outer layers of the SN ejecta leading to a steeper more luminous rise, with bluer colors. Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.

>>>>

\textbf{\citet{2014MNRAS.441..532D} find that DD models are universally faint and red at early times, $\sim$24--48\,hr after explosion, while the PDD models exhibit a faster rise and bluer colors. Briefly, this occurs in the PDD scenario because the collision with the unbound material surrounding the WD heats the outer layers of the SN ejecta. Importantly, the PDD models are nearly indistinguishable from DD models around and post peak.}

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{
  }
  \label{fig:dessart}
\end{figure}

\textbf{In Figure~\ref{fig:dessart} we compare photometric observations of \abc\ to the DD and PDD models presented in \citet{2014MNRAS.441..532D}.}
